Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-07-02 doc/report/msc-report.tex
fixed some comments on the report.

It is suitable to exploit the parallel nature of the records by breaking up
the data sets in pieces and to have each piece be processed on a separate
node in a large compute cluster. It is also suitable to store the data across
many storage nodes in what is called a distributed file system.

@@

Throughout this chapter distinction is made between the developer: who develops
the application, and the user: who uses the product which the developer
creates. Although, in reality, they might be the same person.

@@

Last.fm has a central statistics and metrics tool built on a relational
database. It is possible to import analyzed data to this tool; the data is
presented to the user as graphs. Disadvantages of this system include problems
with new data source additions: they can sometimes not be loaded because they
are too big. If a user wants to perform a custom query, manual intervention by
the developer is necessary. There is no way for this system to handle custom
queries.

@@

At Last.fm there are several different facilities which produce logs, among
them: web servers, scrobbling\footnote{Last.fm users can submit what music they
listen to, this is called scrobbling.}, radio streaming etc. This data reside
on a commodity hardware cluster used for parallel computation. The system needs to
be able to easily import data from these logs, taking in to account both the
locality of the data as well as the structure of the individual data records.

@@

The cardinality of a dimension is the number of distinct values of the
dimension, see it as number of members in a set where the dimension is
viewed as a set. For example, the dimension of \textit{logged in} has a
cardinality of two since \textit{logged in} is a boolean variable; the user
is either logged in or not. The \textit{country} dimension has a much
higher cardinality: there are some 300 countries in the world. Certainly,
there could be dimensions whose cardinality is infinite: the \textit{path}
dimension in the web log example, for example, could in theory have a
limitless number of values.

@@

This section describes how we structured our work over the course of the thesis
project. It describes how we, by working in an exploratory fashion, reached a
good understanding of the problem at hand, and how we successively inched closer
to a working solution by building early prototypes and iteratively improving
upon them.

The design phase, which we entered once our understanding of the problem scope
and its theoretical solution was satisfactory, and the following implementation
are described, followed by a summary of our literature studies.

@@

Only HBase made it this far, the other databases in the roster was hard or
impossible to either compile, install, setup, or all of them.

>>>>

It is appropriate to exploit the parallel nature of the records by breaking up
the data sets in pieces and to have each piece be processed on a separate node
in a large compute cluster. It is also appropriate to store the data across
many storage nodes in what is called a distributed file system.

@@

Throughout this chapter distinction is made between the developer who develops
the application, and the user who uses the product which the developer
creates. Although, in reality, they might be the same person.

@@

Last.fm has a central statistics and metrics tool built on a relational
database. It is possible to import analyzed data to this tool; the data is
presented to the user as graphs. Disadvantages of this system include
\begin{itemize}
\item Problems with new data source additions: they can sometimes not be loaded
because they are too big.
\item If a user wants to perform a custom query, manual intervention by the
developer is necessary.
\item There is no way for this system to handle custom queries.
\end{itemize}

@@

At Last.fm there are several different facilities which produce logs, among
them: web servers, scrobbling\footnote{Last.fm users can submit what music they
listen to, this is called scrobbling.}, radio streaming etc. This data resides
on a commodity hardware cluster used for parallel computation. The system needs to
be able to easily import data from these logs, taking in to account both the
locality of the data as well as the structure of the individual data records.

@@

The cardinality of a dimension is the number of distinct values of the
dimension, see it as number of members in a set where the dimension is
viewed as a set. For example, the dimension of \textit{logged in} has a
cardinality of two since \textit{logged in} is a boolean variable; the user
is either logged in or not. The \textit{country} dimension has a much
higher cardinality: there are some 300 countries in the world. Certainly,
there could be dimensions whose cardinality is unbound: the \textit{path}
dimension in the web log example, for example, could in theory have a
limitless number of values.

@@

This section describes how we structured our work over the course of the thesis
project. It describes how we, by working in an exploratory fashion, reached a
good understanding of the problem at hand, and how we successively moved closer
to a working solution by building early prototypes and iteratively improving
upon them.

The design phase, which we entered once our understanding of the problem scope
and its theoretical solution was satisfactory, and the following implementation
are described, followed by a summary of our tools studies.

@@

Only HBase made it this far, the other databases in the roster were hard or
impossible to either compile, install, setup, or all of them.
